Tugas UAS Kelompok 2

### 2024-06-14 Project/Tugas UAS/Tugas UAS.Rmd

hist(mix_data_1[[1]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
hist(mix_data_1[[2]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
hist(mix_data_1[[3]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
```

@@

```{r fig.height=5, fig.width=15, dpi=300}
set.seed(361)
k <- 1000; n <- 1
mix_data_2 <- rbind(matrix(rchisq(n*k/2, df = 1), k/2), 
                    matrix(rchisq(n*k/2, df = 3), k/2))
hist(mix_data_2, main = "Sebaran Populasi Campuran 2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#96336c")
```

@@

```{r}
t_test_pvalue <- function(x, alt="two.sided", mu = mean(mix_data_1[[1]]) ){
  t.test(x, alternative = alt, mu = mu)$p.value  
}

wilcox_test_pvalue <- function(x,alt="two.sided",mu = mean(mix_data_1[[1]]) ){
  wilcox.test(x, alternative = alt, mu = mu)$p.value  
}
```

@@

>>>>

hist(mix_data_1[[1]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")

hist(mix_data_1[[2]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")

hist(mix_data_1[[3]], main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
```

@@

```{r fig.height=5, fig.width=15, dpi=300}
set.seed(361)

mix_data_2 <- rbind(matrix(rchisq(n*k/2, df = 1), k/2), 
                    matrix(rchisq(n*k/2, df = 3), k/2))
hist(mix_data_2, main = "Sebaran Populasi Campuran 2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#96336c")
```

@@

```{r}
t_test_pvalue <- function(x, alt="two.sided", mu = mean(mix_data_1[[1]] ) ){
  t.test(x, alternative = alt, mu = mu)$p.value  
}

wilcox_test_pvalue <- function(x,alt="two.sided",mu = mean(mix_data_1[[1]] ) ){
  wilcox.test(x, alternative = alt, mu = mu)$p.value  
}
```

@@

```{r}
# membuat objek data.frame dummy untuk menyimpan hasil simulasi
result_sim1 <- data.frame(n=0, alpha_empiris=0, test_name="")
set.seed(2020)
